\paperTitle

### 2014-01-31 doc/icml2014/directed.tex
Minor type fixes

% DONE: move here because not central to story
\paragraph{Remark.} We note that \propertyref{bottleneck} can be relaxed if some cliques
  share parameters.
In the directed grid model, we can identify the conditional moments $O$ from just
  $x^a_1, x^b_1$ and $x^a_2$.
  Therefore, we do not require that $h_2, h_3$ or $h_4$
  be bottlenecks, and can omit the observations $x^b_2, x^b_3$ and $x^b_4$.
%  \todo{make this a footnote if running out of space}
% PL: don't understand this comment
%In this case, we only require that the hidden variables in distinct
  %cliques share parameters.

>>>>

% DONE: move here because not central to story
%\paragraph{Remark.} We note that \propertyref{bottleneck} can be relaxed if some cliques
%  share parameters.
%In the directed grid model, we can identify the conditional moments $O$ from just
%  $x^a_1, x^b_1$ and $x^a_2$.
%  Therefore, we do not require that $h_2, h_3$ or $h_4$
%  be bottlenecks, and can omit the observations $x^b_2, x^b_3$ and $x^b_4$.
%%  \todo{make this a footnote if running out of space}
%% PL: don't understand this comment
%%In this case, we only require that the hidden variables in distinct
%  %cliques share parameters.

### 2014-01-31 doc/icml2014/intro.tex
Minor type fixes

% 1. Latent variable models are good.
Latent-variable graphical models provide compact representations of data
and have been employed across many fields % \todo{find a much better/broader set of citations}
\cite{ghahramani1999variational,jaakkola2011variational,blei03lda,quattoni04crf,beaumont2004bayesian,haghighi06prototype}.
% 2. Learning them is hard.
However, learning these models remains a difficult problem due to the
non-convexity of the negative log-likelihood.  Local methods such as Expectation Maximization (EM)
are the norm, but are susceptible to local optima.

% 3. People have approached unsupervised learning with the MoM magic sauce, but the sauce is limited.
Recently, unsupervised learning techniques based on the spectral method of moments
have offered a refreshing and promising perspective on
this learning problem
\citep{mossel2005learning,
hsu09spectral,
bailly2010spectral,
song2011spectral,
anandkumar11tree,anandkumar12moments,anandkumar12lda,
hsu12identifiability,
balle12automata}.
%\todo{make sure we are citing the right people}
These methods exploit the linear algebraic properties of the model to
factorize the moments into parameters, providing strong theoretical guarantees.
However, these methods apply to a limited set of models, and are thus
not as broadly applicable as EM.

\begin{figure}[t]
  \label{fig:approach}
  \centering
  \subimport{figures/}{approach.tikz}
  \caption{\todo{need three steps: tensor factorization, optimize composite likelihood, recover model parameters;} Overview of approach}
\end{figure}

>>>>

% 1. Latent variable models are good.
Latent-variable graphical models provide compact representations of data
and have been employed across many fields % \todo{find a much better/broader set of citations}
\cite{ghahramani1999variational,jaakkola1999variational,blei03lda,quattoni04crf,beaumont2004bayesian,haghighi06prototype}.
% 2. Learning them is hard.
However, learning these models remains a difficult problem due to the
non-convexity of the negative log-likelihood.  Local methods such as Expectation Maximization (EM)
are the norm, but are susceptible to local optima.

% 3. People have approached unsupervised learning with the MoM magic sauce, but the sauce is limited.
Recently, unsupervised learning techniques based on the spectral method of moments
have offered a refreshing and promising perspective on
this learning problem
\citep{mossel2005learning,
hsu09spectral,
bailly2010spectral,
song2011spectral,
anandkumar11tree,anandkumar12moments,anandkumar12lda,
hsu12identifiability,
balle12automata}.
%\todo{make sure we are citing the right people}
These methods exploit the linear algebraic properties of the model to
factorize the moments into parameters, providing strong theoretical guarantees.
However, they apply to a limited set of models, and are thus
not as broadly applicable as EM.

\begin{figure}[t]
  \label{fig:approach}
  \centering
  \subimport{figures/}{approach.tikz}
  \caption{
 % \todo{need three steps: tensor factorization, optimize composite likelihood, recover model parameters;}
  Overview of approach}
\end{figure}
